---
title: "Assignment: R Markdown and Plotly"
author: "Tong Tat"
date: "December 22, 2017"
output: 
  html_document:
    keep_md: true
    highlight: tango
    theme: yeti
---

**Rpub Link:** [Click Here](http://rpubs.com/chuatt/343727)


# 1. Introduction

This is a document for Coursera Developing Data Product assignment. The objective is to create a web page presentation using R Markdown that features a plot created with Plotly.

The dataset is coming from the **Volcano dataset** coming from the plotly package. I figured since plotly is good at plotting 3D images, so i googled for a dataset that will showcase a 3D image and in this case is a volcano. So here we go!


# 2. Loading Dataset

```{r, warning=FALSE, echo=TRUE, cache=FALSE, message=FALSE}
# Clear cache first
rm(list=ls())

# Check for missing dependencies and load necessary R packages
if(!require(plotly)){install.packages('plotly')}; library(plotly)

# Load dataset
data(volcano)
```


# 3. Data Visualization

Let's take a look at the heatmap of the volcano first. Since the dataset is already available in plotly, we can easily plot the heatmap.

```{r, warning=FALSE, echo=TRUE, cache=FALSE, message=FALSE}
plot.volcano2 <- plot_ly(z = ~volcano) %>% add_heatmap()
plot.volcano2
```


Now, adding on the contours for the volcano.

```{r, warning=FALSE, echo=TRUE, cache=FALSE, message=FALSE}
plot.volcano3 <- plot_ly(z = ~volcano) %>% add_contour()
plot.volcano3
```


Alright, and finally the 3D plot of the volcano.

```{r, warning=FALSE, echo=TRUE, cache=FALSE, message=FALSE}
plot.volcano <- plot_ly(z = ~volcano, type='surface') 
plot.volcano
```